\documentclass{article}


\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.25in]{geometry}


\titleformat{\section}[frame]
{\huge}
{}
{.25em}
{\filcenter\bfseries\lowercase}


\titleformat{\subsection}
{\bfseries\Large}
{\hspace{-.25in}$\bullet$}
{0em}
{}


\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[---]

\titlespacing{\subsubsection}
{0em}{.25em}{1em}


\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}

\vspace{.25em}

luke@lukesmith.xyz --- http://lukesmith.xyz

\end{center}
}




\begin{document}

%This is the resume file we created on my LaTeX resume creation video.

\title{R\'esum\'e}
\author{Luke Smith}

\maketitle

\section{Technical Skills}

\subsection{Work flow}

vim, tmux or a tiling window manager. For networked devices, ssh and either git, rsync or syncthing depending on the need.

\subsection{Languages}

\subsubsection{Programming}

Lisp, Haskell, C, C++

\subsubsection{Scripting}

Python, Perl, shell, R, Praat

\subsubsection{Markup}
{\LaTeX}, HTML, CSS 
\subsection{Multimedia}

\subsubsection{Image}

Most adept volleying between GIMP and imagemagick.

\subsubsection{Video}

I use Blender for video sequencing and FFmpeg for basic operations and screencasting.

\subsubsection{Audio}

FFmpeg or Audacity for basic manipulation. Praat for more advanced or academic purposes. Also familiar with music production software like LMMS.

\section{General Skills}

\subsection{Languages}

\subsubsection{Can speak}

Spanish, Chinese, Latin, some French

\subsubsection{Can read}

Most Romance languages, Greek.

\section{Job experience}

\subsection{University of Arizona}

\subsubsection{Teaching Assistant}

LING300 (Introduction to Syntax), LING150 (Language)

\subsection{University of Georgia}

\subsubsection{Instructor}

LING2100 (Introduction to Linguistics)

\subsubsection{Teaching Assistant}

LING3150 (Generative Syntax)

\section{Service and Other}

\subsection{Academic}

\subsubsection{University of Arizona}

Ran an Indo-European study group.

\subsubsection{University of Georgia}

Managed the second LSUGA linguistics conference, performed video and audio recordings. Created and ran the linguistics club website. Graduate Student Mentor. Ran reading groups on Language Typology and Sociolinguistics.

\subsection{YouTube}

Now I run a YouTube channel mostly on Linux and tech stuff where I make videos like the one I'm making now!

\section{Education}

\subsection{Degrees}

\subsubsection{Ph.D. Linguistics (in progress)}

at the University of Arizona.

\subsubsection{M.A. Linguistics}

at the University of Georgia. Focus on syntax and Romance linguistics.

\subsubsection{B.A. International Economics and Modern Languages}

at Georgia State University. Minors in Chinese and Spanish. Certificates in International Trade and Economic History.

\subsection{Non-degree}

\subsubsection{University of Zhengzhou, Henan}




\end{document}
